Envelope Estimation using Geometric Properties of a Discrete Real Signal

### 2021-05-12 Papers/01_Pulses_Envelope/00ElsevierPulsesEnvelope.tex
revising

\begin{figure}[ht!]
  \centering
    \includegraphics{images/00AlphaShape.pdf}
  \caption{Alpha shape of a set of points for $ \alpha=10 $. A circle of radius 10, containing two points of the set, but defining a disc that does not contain any point of the set, is also shown.}
  \label{fig:AlphaShape}
\end{figure}

@@

The $ \odot $ operator in Equation \ref{eq:Envelope} stands for the Hadamard product and denotes element-wise multiplication of two vectors. Fig. \ref{fig:Envelope} provides an example of the vectors just defined: \textbf{w} is obtained by element-wise multiplication between the normalized carrier wave \textbf{c} and the envelope \textbf{e}.

>>>>

\begin{figure}[ht!]
  \centering
    \includegraphics{images/00AlphaShape.pdf}
  \caption{Alpha shape of a set of points, for $ \alpha=10 $. A circle of radius 10, containing two points of the set, but defining a disc that does not contain any point of the set, is also shown.}
  \label{fig:AlphaShape}
\end{figure}

@@

The $ \odot $ operator in Equation \ref{eq:Envelope} stands for the Hadamard product and denotes element-wise multiplication of two vectors. Fig. \ref{fig:Envelope} provides an example of the vectors just defined: \textbf{w} is obtained by element-wise multiplication between the carrier wave \textbf{c} and the envelope \textbf{e}.
